
\section{Decentralized ranking systems in context}
\subsection{Motivation} 
In this paper, we advance the discussion of voting systems on distributed ledgers such as blockchains. The core benefit of such frameworks is that that vote-casting and voting-result-computation is perfectly transparent and thus always audible.
More concretely, we will not study the consensus protocols enabling the decentralized voting system themselves, but instead review and propose\\
$\bullet$ algorithms for poll evaluations resulting in a sorted lists\\
$\bullet$ innovations made possible through the underlying audible framework

The former can manifest as a mechanisms for the evaluation of opinions invoked by the voters, which, taken together, result in a average ranking. One of our main motivations here is the design of a voting system for a dApps store. So while the subject of the poll algorithms discussed may be anything from politicians to fruits, we will consider the rating of software applications. The vote casting actors will thus be referred to as `users` and correspond to whitelisted addresses on the decentralized ledger. The whitelisting itself need not be result of a decentralized process. 

In this context, the most notable innovation that comes with audible polling is the verifiable claim for rewards based of ``on-chain`` actions. For each poll or voting round, the final result can be put in context with the individual user's vote and thus used to compute a transparent reward claim tied to the user address.

\subsection{Companies that use voting systems}

\subsection{Requirements for NOS in comparison to what other companies use}
what's different here 

a) blockchain consensus 

b) dApp rankings 

c) Gain from being votes high up.

\section{Scientific view}
\subsection{properties of voting systems (viewed on their own)} % wie im Satz
\subsection{rule out and classify for the means of a) and b)}

\subsection{existing voting systems}
\subsection{differentiation; part of upper subsection}

\section{economical perspective} %?????????????????????????????

\section{how the properties apply for other companies and how steemit is bad etc}

\section{propose an algorithm}



